---
title: "Task 2  Iris dataset"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### importing ***ggplot & cluster*** library
```{r}
library(ggplot2)
library(cluster)
```
### Read the dataset from the csv file
``` {r}
task2 <- read.csv("iris.csv")
print(task2)
```
```{r}
library(ggplot2)
```

## Plotting graph between PetalLengthCm and  PetalWidthCm
```{r}
ggplot(task2, aes(PetalLengthCm, PetalWidthCm)) + geom_point(aes(col=Species), size=4)
```


## Plotting graph between SepalLengthCm and  SepalWidthCm
```{r}
ggplot(task2, aes(SepalLengthCm, SepalWidthCm)) + geom_point(aes(col=Species), size=4)

 

```
### Summary of the given dataset
```{r}
summary(task2)
head(task2)
```
### Extracting the features
```{r}
k<- c("SepalLengthCm","SepalWidthCm","PetalLengthCm","PetalWidthCm")
df = task2[k]
print(df)
```
### Optimal number of cluster in Dataset
```{r}
twss <- vector(mode="character", length=10)
for (i in 1:10){
  irisCluster <- kmeans(df, center=i, nstart=20)
  twss[i] <- irisCluster$tot.withinss
}
plot(1:10, twss, type="b", pch=19)
```

We are able to see that total within sum of square value is significant between 2 & 3 as compared to 3 & 4.
So, we will take **3 as the number of clusters.**

### Plotting
```{r}
df <- kmeans(df[,1:4], center=3, nstart=20)
clusplot(iris, df$cluster, color=T, shade=T, labels=0, lines=0)
```